### 2014-05-21 remy_limits.tex
Small fixes
Fill in Ratatouille screenshot

We think this tradeoff is ultimately worth taking: today's endpoints
can execute complex algorithms almost as easily as simple ones, and
the \textit{computational} complexity of a RemyCC is low in any event.

But when endpoint algorithms become so complex, it is challenging to
explain \emph{why} a particular RemyCC works without considerable
effort spent reverse-engineering it. To help with this task, I built a
visualization and debugging tool for RemyCCs, called Ratatouille.

@@

Examining the RemyCCs that are successful in the simulations we
evaluated, we found that the period of the limit cycles is generally a
small number of minRTTs. By contrast, TCP's congestion window
generally oscillates on a much longer timescale that depends on the
buffer size, because the ``multiplicative decrease'' feature of TCP's
control rules is only triggered when packet loss is detected (in other
words, only after buffer overflow occurs in the bottleneck queue).

Our observations suggest that a RemyCC's ability to achieve better
throughput than TCP on finite-length flows is mostly due to its
quicker response to changes in conditions---a RemyCC will generally
``ramp up'' to the ideal number of packets-in-flight more quickly than
the TCP slow-start algorithm.

@@

\begin{figure}
\caption{Ratatouille allows a user to vary network conditions on a
  physical control service, then observe the resulting behavior of a
  RemyCC in real-time.}
\label{fig:ratscreen}

@@

(XXX insert screenshot)

>>>>

We think this tradeoff is ultimately worth taking: today's endpoints
can execute complex algorithms almost as easily as simple ones, and
the \textit{computational} complexity of a RemyCC is low in any
event. But when endpoint algorithms become so complex, it is
challenging to explain why a particular RemyCC works without
considerable effort spent reverse-engineering it. To help with this
task, I built a visualization and debugging tool for RemyCCs, called
Ratatouille.

@@

The period of the limit cycle is generally a small number of RTTs. By
contrast, TCP's congestion window generally oscillates on a much
longer timescale that depends on the buffer size, because the
``multiplicative decrease'' feature of TCP's control rules is only
triggered when packet loss is detected, typically only after buffer
overflow occurs in the bottleneck queue.

Our observations suggest that a RemyCC's ability to achieve better
throughput than TCP on finite-length flows is mostly due to its
quicker response to changes in conditions---a RemyCC will generally
``ramp up'' to the ideal number of packets-in-flight more quickly than
the TCP slow-start algorithm (Figure~\ref{fig:ratscreen}).

@@

\begin{figure}
\caption{Ratatouille allows a user to vary network conditions on a
  physical control service, then observe the resulting behavior of a
  RemyCC in real-time. Below, the initial startup and steady-state
  behavior of the RemyCC-100x algorithm of Section~\ref{s:oprangeperftradeoff}.}
\label{fig:ratscreen}

@@

\includegraphics[width=0.85 \textwidth]{ratatouille.png}
